Discovery of s-process stars in the LAMOST survey

### 2018-01-24 article/ms.tex
spelling

The slow neutron capture process (s-process), occuring in the interior of AGB stars, synthesizes roughly half of all elements heavier than iron \citep[e.g.][]{busso1999,travaglio2001,herwig2005,romano2010,kobayashi2011,prantzos2012,bisterzo2014,karakas12016}. Late in the AGB phase, during the thermally pulsing-AGB (TP-AGB) phase, thermal instabilities occur in the He shell every $10^5$ years or so, depending on the H-exhausted core mass. These energy bursts drive a convective zone that sweeps the entire region lying between the core mass and He-shell; mixing the products of nucleosynthesis within these regions. The energy from the thermal pulses force the star to expand, pushing the H-shell out to cooler regions and allowing the convective envelope to move inwards to regions previously mixed by the thermal pulse driven convective zones. This expansion and resultsing inward movement is classified as the third dredge up (TDU), and is theorised to occur after each thermal pulse. During the TP-AGB phase, enrichent on the surface in $^{12}$C and heavy elements produced by the s-process is a result of the repeated downwash extensions of TDU \citep[e.g.][]{busso2001}. The star contracts PDU and reignites the H-shell producing the majority of the surface luminosity for the next interpulse period. The interpulse, thermal pulse, and dredge up cycle may occur numerous times and is dependent on the intitial mass, composition, and mass-loss rate of the star.

>>>>

The slow neutron capture process (s-process), occurring in the interior of AGB stars, synthesises roughly half of all elements heavier than iron \citep[e.g.][]{busso1999,travaglio2001,herwig2005,romano2010,kobayashi2011,prantzos2012,bisterzo2014,karakas12016}. Late in the AGB phase, during the thermally pulsing-AGB (TP-AGB) phase, thermal instabilities occur in the He shell every $10^5$ years or so, depending on the H-exhausted core mass. These energy bursts drive a convective zone that sweeps the entire region lying between the core mass and He-shell; mixing the products of nucleosynthesis within these regions. The energy from the thermal pulses force the star to expand, pushing the H-shell out to cooler regions and allowing the convective envelope to move inwards to regions previously mixed by the thermal pulse driven convective zones. This expansion and resulting inward movement is described as the third dredge up (TDU), and is theorised to occur after each thermal pulse. During the TP-AGB phase, enrichment on the surface in $^{12}$C and heavy elements produced by the s-process is a result of the repeated downwash extensions of TDU \citep[e.g.][]{busso2001}. The star contracts PDU and reignites the H-shell producing the majority of the surface luminosity for the next interpulse period. The interpulse, thermal pulse, and dredge up cycle may occur numerous times and is dependent on the initial mass, composition, and mass-loss rate of the star.
